\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-12-12 main.tex
work on writing hierarical structure and example

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_nested <- cubble::climate_flat %>%
+   as_cubble(key = id, index = date, coords = c("long", "lat")))
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_long <- cubble_nested %>% stretch(ts))
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin
   <chr>       <date>     <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3
 2 ASN00009021 2020-01-02     0  24.9  16.4
 3 ASN00009021 2020-01-03     6  23.2  13  
 4 ASN00009021 2020-01-04     0  28.4  12.4
 5 ASN00009021 2020-01-05     0  35.3  11.6
 6 ASN00009021 2020-01-06     0  34.8  13.1
 7 ASN00009021 2020-01-07     0  32.8  15.1
 8 ASN00009021 2020-01-08     0  30.4  17.4
 9 ASN00009021 2020-01-09     0  28.7  17.3
10 ASN00009021 2020-01-10     0  32.6  15.8
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_back <- cubble_long %>% tamp())
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_long %>% migrate(long, lat))
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin  long   lat
   <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
 2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
 3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
 4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
 5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
 6 ASN00009021 2020-01-06     0  34.8  13.1  116. -31.9
 7 ASN00009021 2020-01-07     0  32.8  15.1  116. -31.9
 8 ASN00009021 2020-01-08     0  30.4  17.4  116. -31.9
 9 ASN00009021 2020-01-09     0  28.7  17.3  116. -31.9
10 ASN00009021 2020-01-10     0  32.6  15.8  116. -31.9
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\texttt{switch\_key()}

@@

Bureau of Meteorology (BoM) collects climate variables. This variables
can be openly queried via \texttt{rnoaa}. \texttt{weatherdata} provides
a readily available copy of several data.
\texttt{weatherdata::historical\_tmax} provides historical maximum
temperature recorded for Australian stations with the earliest dating
back to 1859 and this can be used to understand the change of maximum
temperature from a past period to nowadays.

@@

\caption[demon code]{demon code}\label{fig:code1-workflow}
\end{figure}
\end{CodeChunk}

\begin{center}\includegraphics{figures/unnamed-chunk-6-1} \end{center}

@@

On top of \texttt{aus\_climate} data in this package,
\texttt{climate\_full} from package
\href{https://github.com/huizezhang-sherry/weatherdata}{\texttt{weatherdata}}
has daily climate data of 639 Australia stations from 2016 to 2020. This
is where these stations locate in an Australia map:

This is a lot of stations to look at for one climate variable and they
can't all fit into a glyph map. What we can do is to group stations into
clusters and look at the aggregated series in the glyph map. In this
vignette, I will introduce how to perform spatial (and temporal)
aggregation using hierarchical data structure in cubble.

First let's add a new column \texttt{ll} for calculating distance matrix
in the next section and aggregate the daily precipitation into weekly
measure. These steps should be familiar from the vignette \emph{Data
manipulation with cubble}.

\begin{CodeChunk}
\begin{CodeInput}
R> station_nested <- weatherdata::climate_full %>%
+   mutate(ll = s2::s2_lnglat(long, lat)) %>%
+   stretch() %>%
+   mutate(wk = lubridate::week(date)) %>%
+   group_by(wk) %>%
+   summarise(prcp = sum(prcp, na.rm = TRUE)) %>%
+   tamp()
\end{CodeInput}
\end{CodeChunk}

Imposing a clustering structure can be thought of as building a
hierarchical structure where stations are nested within clusters. As an
example to illustrate here, we use a kmean clustering algorithm based on
the distance matrix and specify the number of centres to be 20. More
complex algorithms can also be used for more complex problem, as long as
a mapping from each station id to the cluster id can be constructed. We
then join this data to our station data:

\begin{CodeChunk}
\begin{CodeInput}
R> dist_raw <- scale(s2::s2_distance_matrix(station_nested$ll, station_nested$ll))
R> 
R> cluster_res <- tibble(
+   id = station_nested$id,
+   cluster = kmeans(dist_raw, centers = 20, nstart = 50)$cluster
+ )
R> 
R> station_nested <- station_nested %>%
+   left_join(cluster_res)
\end{CodeInput}
\end{CodeChunk}

One thing we hope to do with the cluster is to find the coordinates of
the centroid. These are variables variant to the station but invariant
to the cluster and it would be nice to have a function that structure
each cluster as a row. \texttt{switch\_key()} is the function that does
this: it lets you to specify a new key, say \texttt{cluster} and nests
all spatial variables variant to \texttt{cluster} into a column.
Temporal observations from different stations while within the same
cluster are bound in the nested column \texttt{ts}.

\begin{CodeChunk}
\begin{CodeInput}
R> cluster_nested <- station_nested %>%
+   switch_key(cluster)
\end{CodeInput}
\end{CodeChunk}

This structure makes it easy to compute cluster level variable, although
there are a few steps to calculate the centroid coordinates: we need to
find the convex hull that wraps around the cluster, make it a polygon,
find the centroid of the polygon and finally, extract the x and y
coordinate of each centroid:

\begin{CodeChunk}
\begin{CodeInput}
R> cluster_nested <- cluster_nested %>%
+   mutate(
+     chull = list(chull(.val$long, .val$lat)),
+     ll_cluster = sf::st_as_sfc(
+       s2::s2_make_polygon(c(.val$long[chull]),
+         c(.val$lat[chull]),
+         oriented = FALSE
+       )
+     ),
+     centroid = s2::s2_centroid(ll_cluster),
+     cent_long = s2::s2_x(centroid),
+     cent_lat = s2::s2_y(centroid)
+   )
\end{CodeInput}
\end{CodeChunk}

After we have got \texttt{cluster\_nested}, spatial and temporal data at
both levels can be easily obtained. If we use \texttt{station} and
\texttt{cluster} prefix to denote the two levels and \texttt{nested} and
\texttt{long} for whether the data shows the spatial or temporal
dimension, the relationship among the four datasets can be illustrated
in the following workflow:

Start with the original \texttt{station\_nested}, \texttt{stretch()}
expands the \texttt{ts} column with each station (\texttt{id}) forming a
group and attach variables invariant to \texttt{id} as an attribute.
\texttt{switch\_key()} changes the \texttt{key} from \texttt{id} to
\texttt{cluster} and nests all the spatial variables that variant to
\texttt{cluster}. \texttt{stretch()} \texttt{cluster\_nested} will store
variables that are invariant to \texttt{cluster} as a tibble in the
attribute.

Now we can obtain the aggregated series as described in the workflow
diagram above and construct the glyph map with
\texttt{GGally::glyphs()}:

\begin{center}\includegraphics{figures/unnamed-chunk-11-1} \end{center}

We can also look at the precipitation of each individual station within
the same cluster:

@@

{\centering \includegraphics{figures/unnamed-chunk-12-1}

@@

\caption[shtishisa]{shtishisa}\label{fig:unnamed-chunk-12}
\end{figure}
\end{CodeChunk}

Lastly, there is one series on Tasmania island standing out from others,
lets look at where it is:

\begin{center}\includegraphics{figures/unnamed-chunk-13-1} \end{center}

@@

\begin{center}\includegraphics{figures/unnamed-chunk-14-1} \end{center}

@@

{\centering \includegraphics{figures/unnamed-chunk-15-1}

@@

\caption[shtishisaasdf]{shtishisaasdf}\label{fig:unnamed-chunk-15}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> river <- river %>%
+   stretch() %>%
+   rename(prcp = Water_course_level) %>%
+   tamp()
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> res <- match_sites(river, climate,
+   temporal_var_to_match = prcp,
+   temporal_independent = climate,  
+   temporal_n_highest = 30,
+   temporal_min_match = 15
+ )
R> 
R> res
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [8]: nested form
# bbox:     [144.52, -37.73, 146.06, -36.55]
# temporal: date [date], prcp [dbl]
  id          name                lat  long type  ts        .dist .group n_match
  <chr>       <chr>             <dbl> <dbl> <chr> <list>    <dbl>  <int>   <int>
1 405234      SEVEN CREEKS @ D~ -36.9  146. river <tibble ~  6.15      5      21
2 ASN00082042 strathbogie       -36.8  146. clim~ <tibble ~  6.15      5      21
3 404207      HOLLAND CREEK @ ~ -36.6  146. river <tibble ~  8.54     10      21
4 ASN00082170 benalla airport   -36.6  146. clim~ <tibble ~  8.54     10      21
5 230200      MARIBYRNONG RIVE~ -37.7  145. river <tibble ~  6.17      6      19
6 ASN00086038 essendon airport  -37.7  145. clim~ <tibble ~  6.17      6      19
7 406213      CAMPASPE RIVER @~ -37.0  145. river <tibble ~  1.84      1      18
8 ASN00088051 redesdale         -37.0  145. clim~ <tibble ~  1.84      1      18
\end{CodeOutput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{figures/unnamed-chunk-18-1}

@@

\caption[..]{...}\label{fig:unnamed-chunk-18}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> nc <- ncdf4::nc_open(here::here("data/adaptor.mars.internal-1638344933.932894-4194-11-a5d35ac3-b36d-4982-afa5-a5dd193a6718.nc"))
R> 
R> nc <- ncdf4::nc_open(here::here("data/tas_Amon_ACCESS-CM2_ssp585_r1i1p1f1_gn_20150116-20201216_v20191108.nc"))
R> temp <- as_cubble(nc, vars = "tas")
R> vic_map <- ozmaps::abs_ste %>% filter(NAME == "Victoria")
R> 
R> res <- temp %>% 
+   stretch(ts) %>% 
+   mutate(d2m = d2m - 273.15) %>% 
+   filter(lubridate::hour(time) == 12) %>% 
+   group_by(id) %>% 
+   summarise(d2m = mean(d2m, na.rm= TRUE)) %>%
+   migrate(long, lat)
R> 
R> vic_string <- vic_map %>% sf::st_cast("MULTILINESTRING") 
R> 
R> res %>% 
+   ggplot() +
+   geom_tile(aes(x = long, y = lat, fill = d2m)) +
+   geom_sf(data = vic_string , alpha = 0.5, fill = "transparent") +
+   theme_bw() + 
+   colorspace::scale_fill_continuous_sequential("Mint")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> climate_flat %>% as_cubble(key = id, index = date, coords = c(long, lat))
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> sydmel_climate <- stations %>%
+   rowwise() %>%
+   mutate(ts = list(meteo_pull_monitors(id,
+     date_min = "2020-01-01",
+     date_max = "2020-12-31",
+     var = c("PRCP", "TMAX", "TMIN")
+   ) %>%
+     select(-id))) %>%
+   as_cubble(key = id, index = date, coords = c(long, lat))
\end{CodeInput}
\end{CodeChunk}

>>>>

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin
   <chr>       <date>     <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3
 2 ASN00009021 2020-01-02     0  24.9  16.4
 3 ASN00009021 2020-01-03     6  23.2  13  
 4 ASN00009021 2020-01-04     0  28.4  12.4
 5 ASN00009021 2020-01-05     0  35.3  11.6
 6 ASN00009021 2020-01-06     0  34.8  13.1
 7 ASN00009021 2020-01-07     0  32.8  15.1
 8 ASN00009021 2020-01-08     0  30.4  17.4
 9 ASN00009021 2020-01-09     0  28.7  17.3
10 ASN00009021 2020-01-10     0  32.6  15.8
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin  long   lat
   <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
 2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
 3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
 4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
 5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
 6 ASN00009021 2020-01-06     0  34.8  13.1  116. -31.9
 7 ASN00009021 2020-01-07     0  32.8  15.1  116. -31.9
 8 ASN00009021 2020-01-08     0  30.4  17.4  116. -31.9
 9 ASN00009021 2020-01-09     0  28.7  17.3  116. -31.9
10 ASN00009021 2020-01-10     0  32.6  15.8  116. -31.9
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

Imposing a clustering structure can be thought of as building a
hierarchical structure where stations are nested within clusters. This
can be useful when there's intrinsic nesting structure in the data
(i.e.~country nested in the continent, county nested in the state) or
there's some clustering. When we have access to both level,
\texttt{switch\_key()} is the function to re-structure the data as one
cluster per row. Temporal observations from different stations while
within the same cluster are bound in the nested column \texttt{ts}.

One thing we hope to do with the cluster is to find the coordinates of
the centroid. These are variables variant to the station but invariant
to the cluster and it would be nice to have a function that structure
each cluster as a row. \texttt{switch\_key()} is the function that does
this: it lets you to specify a new key, say \texttt{cluster} and nests
all spatial variables variant to \texttt{cluster} into a column. Spatial
variables are all nested inside a new column \texttt{.val}. Temporal
observations from different stations while within the same cluster are
bound in the nested column \texttt{ts}.

This structure makes it easy to compute cluster level variable, for
example, the convex hull and the centroid coordinate of each cluster.
These can be amended into the nested form with function
\texttt{get\_centroid}.

After we have got \texttt{cluster\_nested}, spatial and temporal data at
both levels can be easily obtained. Figure \ref{fig:hierachical}
illustrate the relationship between the long and nested form cubble at
both site and cluster level. More description on this. Start with the
original \texttt{station\_nested}, \texttt{stretch()} expands the
\texttt{ts} column with each station (\texttt{id}) forming a group and
attach variables invariant to \texttt{id} as an attribute.
\texttt{switch\_key()} changes the \texttt{key} from \texttt{id} to
\texttt{cluster} and nests all the spatial variables that variant to
\texttt{cluster}. \texttt{stretch()} \texttt{cluster\_nested} will store
variables that are invariant to \texttt{cluster} as a tibble in the
attribute.

this fit into the remaining data pipeline.

@@

Bureau of Meteorology (BoM) collects climate variables. This variables
can be openly queried via \texttt{rnoaa}. \texttt{weatherdata} provides
a readily available copy of several
data.\texttt{weatherdata::historical\_tmax} provides historical maximum
temperature recorded for Australian stations with the earliest dating
back to 1859 and this can be used to understand the change of maximum
temperature from a past period to nowadays. Figure
\ref{fig:glyphmap-workflow} shows the steps involved from the initial
data to the final glyph map in Figure \ref{fig:glyphmap}.

@@

\caption[demon code]{demon code}\label{fig:glyphmap-workflow}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{figures/basic-manipulation}

\caption[asdfasd]{asdfasd}\label{fig:glyphmap}
\end{figure}
\end{CodeChunk}

@@

In figure \ref{fig:glyphmap}, there are a few stations around Sydney
(151E, 34S) and New castle (152E, 33S). Aggregating them into averages
or other statistics would give a better picture. This can be done with
cubble through a hierarchical structure, where the cluster indicator is
one level above the individual station.

In Figure \ref{fig:aggregation}

The \texttt{weatherdata::climate\_full} data has daily climate data of
639 Australia stations from 2016 to 2020.

calcluate distance matrix As an example to illustrate here, a kmean
clustering algorithm based on the distance matrix is used and the number
of centres is set to 20. More complex algorithms can also be used for
more complex problem, as long as a mapping from each station id to the
cluster id can be constructed.

@@

{\centering \includegraphics[width=1\linewidth,height=0.9\textheight]{figures/aggregation}

@@

\caption[sdfasdf]{sdfasdf}\label{fig:aggregation}
\end{figure}
\end{CodeChunk}

@@

\begin{center}\includegraphics{figures/unnamed-chunk-7-1} \end{center}

@@

{\centering \includegraphics{figures/unnamed-chunk-8-1}

@@

\caption[shtishisaasdf]{shtishisaasdf}\label{fig:unnamed-chunk-8}
\end{figure}
\end{CodeChunk}

@@

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [8]: nested form
# bbox:     [144.52, -37.73, 146.06, -36.55]
# temporal: date [date], prcp [dbl]
  id          name                lat  long type  ts        .dist .group n_match
  <chr>       <chr>             <dbl> <dbl> <chr> <list>    <dbl>  <int>   <int>
1 405234      SEVEN CREEKS @ D~ -36.9  146. river <tibble ~  6.15      5      21
2 ASN00082042 strathbogie       -36.8  146. clim~ <tibble ~  6.15      5      21
3 404207      HOLLAND CREEK @ ~ -36.6  146. river <tibble ~  8.54     10      21
4 ASN00082170 benalla airport   -36.6  146. clim~ <tibble ~  8.54     10      21
5 230200      MARIBYRNONG RIVE~ -37.7  145. river <tibble ~  6.17      6      19
6 ASN00086038 essendon airport  -37.7  145. clim~ <tibble ~  6.17      6      19
7 406213      CAMPASPE RIVER @~ -37.0  145. river <tibble ~  1.84      1      18
8 ASN00088051 redesdale         -37.0  145. clim~ <tibble ~  1.84      1      18
\end{CodeOutput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{figures/unnamed-chunk-11-1}

@@

\caption[..]{...}\label{fig:unnamed-chunk-11}
\end{figure}
\end{CodeChunk}

@@

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

@@
